### 2023-11-15 related.tex
Updates from Overleaf

For systems rooted in constraint solving, there has been considerable work in improving error localization because such systems are notorious for making error localization difficult, and programmers are often confused by localization decisions \cite{wand1986} because they are rooted in \emph{ad hoc} traversal orders \cite{mcadam1999,lee1998}. 
More recently, there has been a series of papers that discuss finding the most likely location for an error based on maximum likelihood estimation \cite{zhang2014} or manual/learned weights \cite{pavlinovic2014,seidel2017}.
While improving the situation somewhat, these remain fundamentally \emph{ad hoc} in their need to guess intent. However, data-driven approaches could perhaps be layered atop type hole inference to improve the ranking or filtering of suggestions.

@@

In the realm of error messages for constraint-based inference, work on the Helium Haskell compiler \cite{heeren2003} offers two constraint solvers based on the desired feedback: a global, type graph-based constraint solver which provides detailed error messages, and a lightweight and high-performance greedy solver. When using the global constraint solver, various heuristics can tune the likelihood of different parts of programs reported as error sources.
Recently, \citet{bhanuka2023} model the flow of type information throughout the program using subtyping constraints to produce detailed error messages when unification fails.
Our focus in this paper has not been on the error messages displayed on-screen, about which we make no specific claims.
It may, however, be beneficial to indicate to the user from where in the program type suggestions originated via type provenances. Documenting the flow of type information would require using asymmetric constraints rather than typical bidirectional equality constraints.

In addition, there has been considerable work on improving explanations for type errors, e.g., by providing sample inputs (dynamic witnesses) that elicit runtime errors \cite{seidel2016}. With this approach, one can generate graphs for visualizing the execution of witnesses and heuristically identify the source of errors with around 70\% accuracy.
These and a variety of other approaches to explaining errors are a fruitful avenue for future integration into the system.

>>>>

For systems rooted in constraint solving, there has been considerable work in improving error localization because such systems are notorious for making error localization difficult, and programmers are often confused by localization decisions \cite{wand1986} because they are rooted in \emph{ad hoc} traversal orders \cite{mcadam1999,lee1998}. 
More recently, there has been a series of papers that discuss finding the most likely location for an error based on a maximum likelihood criterion applied to type flows \cite{zhang2014} or manual/learned weights \cite{pavlinovic2014,seidel2017}.
While improving the situation somewhat, these remain fundamentally \emph{ad hoc} in their need to guess intent. However, data-driven approaches could perhaps be layered atop type hole inference to improve the ranking or filtering of suggestions.

@@

In the realm of error messages for constraint-based inference, work on the Helium Haskell compiler \cite{heeren2003} offers two constraint solvers based on the desired feedback: a global, type graph-based constraint solver which provides detailed error messages, and a lightweight and high-performance greedy solver. When using the global constraint solver, various heuristics can tune the likelihood of different parts of programs reported as error sources.
Recently, \citet{bhanuka2023} model the flow of type information throughout the program using subtyping constraints to produce detailed error messages when unification fails. \citet{seidel2016} provide sample inputs (dynamic witnesses) that elicit runtime errors. With this approach, one can generate graphs for visualizing the execution of witnesses and heuristically identify the source of errors with around 70\% accuracy.
Our focus in this paper has not been on the error messages displayed on-screen, about which we make no specific claims.
It may, however, be beneficial in future work to indicate to the user from where in the program type suggestions originated via type provenances and by incorporating the techniques in this prior work, e.g. to explain why a particular suggestion arises. Documenting the flow of type information would require using asymmetric constraints rather than typical bidirectional equality constraints.
